FoRTE baseline

### 2019-04-17 analysis/paper/paper.Rmd
Add more notes and references to paper
Many updates for reading ensemble output, plus some paper notes

@@

Light availability is a first order control on photosynthesis, and competition for light is a key process in driving competitive dynamics and community succession.
How light is distributed through a canopy is therefore critically important to accurately simulating community dynamics.
Radiative transfer models are used to simulate light proliferation through a canopy.
Detailed, 3D representations [@widlowski_2014_abstract; @widlowski_2007_third; @malenovsky_2008_influence] have prohibitively high computational costs for use in dynamic vegetation models.
Therefore, these models have had to rely on computationally-efficient approximations.
One common approach is the "two-stream approximation", originally developed for atmospheric radiative transfer [@meador_1980_two] and later adapted for plant canopies [@dickinson_1983_land; @sellers_1985_canopy].
<!-- TODO: Further discussion? -->
Although popular, the two-stream approach has some important limitations (REFS, details...).
An alternative approach is the "multiple scattering" model of @zhao_2005_multiple.
Accounting for multiple scattering enhances canopy light absorption, particularly in near-infrared wavelengths [@zhao_2005_multiple], therefore reducing the amount of light that makes it into the understory (TODO confirm).
<!-- TODO: Further discussion -->

@@

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
    - For details, see Supplements S9 and S10 in [@longo_2019_ed1].
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation

@@

>>>>

[@rollinson_2017_emergent] -- ED2 paleoclimate
[@miller_2015_alteration] -- ED2 at Duke FACE
[@dekauwe_2013_forest] -- ED2 at Duke and Oak Ridge FACE

@@

Light availability is a first order control on photosynthesis, and competition for light is a key process in driving competitive dynamics and community succession [@bazzaz_1979_physiological].
How light is distributed through a canopy is therefore critically important to accurately simulating community dynamics.
Radiative transfer models are used to simulate light proliferation through a canopy.
Detailed, 3D representations [@widlowski_2014_abstract; @widlowski_2007_third; @malenovsky_2008_influence] have prohibitively high computational costs for use in dynamic vegetation models.
Therefore, these models have had to rely on computationally-efficient approximations.
One common approach is the "two-stream approximation", originally developed for atmospheric radiative transfer [@meador_1980_two] and later adapted for plant canopies [@dickinson_1983_land; @sellers_1985_canopy].
<!-- TODO: Further discussion? -->
Although popular, the two-stream approach has some important limitations (REFS, details...).
An alternative approach is the "multiple scattering" model of @zhao_2005_multiple.
Accounting for multiple scattering enhances canopy light absorption, particularly in near-infrared wavelengths [@zhao_2005_multiple], therefore reducing the amount of light that makes it into the understory (TODO confirm).
<!-- TODO: Further discussion -->

@@

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
    - For details, see Supplements S9 and S10 in [@longo_2019_ed1].
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation
    - V~cmax~(0) decline with shade tolerance is supported by classic ecological theory on succession [@bazzaz_1979_physiological]

@@

## Analysis of results

Photosynthesis / respiration ratio (i.e. C balance) in light and shade can be used as an indication of succession -- expect early successional species to have higher ratio in light and late successional species to have higher ratio in shade [@bazzaz_1979_physiological].
